\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx}
\usepackage[justification=centering,labelfont=bf]{caption}
\usepackage{listings}


\newcommand{\blueline}[1]{\textcolor{blue}{#1}}

\newcommand{\assignatura}{Parallelism}
\newcommand{\titol}{Second Deliverable}

\newcommand{\Pautor}{Héctor Ramón Jiménez}
\newcommand{\Sautor}{Alvaro Espuña Buxó}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\newcounter{ProblemCounter}
\newcommand{\question}{%
  \setcounter{enumi}{\value{ProblemCounter}}%
  \stepcounter{ProblemCounter}%
}
\newcommand{\answer}[1]{
  {\bf {#1}}
}

\begin{document}

\begin{titlepage}
  \begin{center}
    \textsc{\Large \assignatura}\\
    \texttt{1202}\\[1.5cm]
    \HRule \\[0.4cm]
     { \huge \bfseries \titol \\[0.4cm] }
    \HRule \\[2.5cm]
    \begin{minipage}{0.4\textwidth}
      \begin{flushleft}
        \large \Pautor
      \end{flushleft}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
      \begin{flushright}
        \large \Sautor
      \end{flushright}
    \end{minipage}

    \vfill
    {\large \today} \\
    {\large \texttt{Facultat d'Informàtica de Barcelona}}
  \end{center}
\end{titlepage}

\section*{Parallelization overheads}
\begin{enumerate}
  \question \item Which is the overhead associated with the activation
  of a parallel region in OpenMP? Is it constant?  Reason the answer
  based on the results reported by the ompparallel code and the the
  trace visualized with Paraver.

  \answer{
  }

  \question \item Which is the minimum overhead associated with the
  execution of critical regions in OpenMP?

  \answer{
  }

  \question \item In the presence of lock conflicts and true sharing
  (as it happens in dotprod mutex everytime), how the overhead
  associated with critical increases with the number of processors?
  How this overhead is decomposed? Reason the answer based on the
  results visualized with Paraver.


  \answer{
  }


  \question \item In the presence of false sharing (as it happens in
  dotprod vectorsum), which is the additional average access latency
  that you observe to memory? Which causes this increase in the memory
  access time? Reason the answer based on the results visualized with
  Paraver.

  \answer{
  }


\end{enumerate}

\clearpage
\section*{Execution time and speed-up}
\begin{enumerate}
  \question \item Complete the following table with the execution
  times of the different versions of dotprod that we provide to
  you. The speed–up has to be computed with respect to the execution
  of the serial version. For each version and number of threads, how
  many executions have you performed?

  \begin{center}
  \begin{tabular}{| l || c | c | c|}
    \hline
    {\bf version} & {\bf 1 processor} & {\bf 8 processors} & {\bf speed-up}
    \hline\hline
    dotprod\_serial & & & h\\
    \hline
    dotprod\_mutex\_everytime & & & h \\
    \hline
    dotprod\_mutex & & & h\\
    \hline
    dotprod\_vectorsum & & & h \\
    \hline
    dotprod\_vectorsum\_padding & & & h \\
    \hline
  \end{tabular}
  \end{center}

\end{enumerate}

\end{document}
